\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-23 WOOT/Files/related_work.tex
minor change of related work

\subsection{USB Attack}
\label{subsec:usb_attack}
\chaozu{DoS(Fuzzing), Code injection, HID emulation, JFC, our work}
During the development of USB protocol, there are many USB-based attacks were proposed, ranging from DoS (denial of service) to protocol masquerading. Here we will introduce them following an order of their category.

@@

Since USB 3.1 was introduced with USB Type-C in 2013, display port and HDMI connectors have been provided by USB Type-C, transformation for video streaming data is guaranteed with the other attacks, e.g., protocol masquerading,  protocol corruption and code injection. This allows attacker to control users' devices with screen monitoring, attacks for interaction work here.

>>>>

\subsection{USB Attack}
\label{subsec:usb_attack}
\chaozu{DoS(Fuzzing), Code injection, HID emulation, JFC, our work}
During the development of USB protocol, there are many USB-based attacks were proposed, ranging from DoS (denial of service) to protocol masquerading. Here we will introduce them following an order of their category.\hongyi{What?}

@@

Since USB 3.1 was introduced with USB Type-C in 2013, display port and HDMI connectors have been provided by USB Type-C, transferring of video data can be combined with the other attacks, like protocol masquerading,  protocol corruption and code injection. This has paved the path for our \tool.
